---
title: "Class 13: Visualizing Campaign Finance data"
author: "FIRSTNAME LASTNAME"
date: "`r format(Sys.time(), '%B %d, %Y')`"
time: "`r format(Sys.time(), '%H:%M')`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Instructions
Today in class we will begin dealing with messy text data -- names, professions and employers in the campaign finance data.


###Load the tidyverse package(s)
Also, explicitly load stringr package.
And install _and_ load htmlwidgets package, which is a dependentcy of a lot of the coolest things in stringr.
```{r}
#install.packages("tidyverse")
library(tidyverse)
library(stringr)
#install.packages("htmlwidgets")
library(htmlwidgets)
```


###Load the data 
```{r}

#url <- "https://cf.ncsbe.gov/CFOrgLkup/ExportDetailResults/?ReportID=168216&Type=REC&Title=Cooper%20for%20North%20Carolina%20-%202019%20Mid%20Year%20Semi-Annual"

#read_csv() does not do a great job here guessing the correct col_types, so we have to define them explicitly.

#cooper_rcpts_2019A <- read_csv(url, 
#    col_types = cols(
#      `Account Abbr` = col_character(), 
#        City = col_character(), 
#      `Country Name` = col_character(), 
#        Date = col_date(format = "%m/%d/%Y"), 
#        Description = col_character(), 
#      `Employers Name` = col_character(), 
#        `Full Zip` = col_character(), 
#      `Outside US Postal Code` = col_character(), 
#        Profession = col_character(), 
#      Purpose = col_character(), 
#        State = col_character(), 
#      `Street 1` = col_character(), 
#        `Street 2` = col_character()),
#    skip = 1)

#Finally, we should rename the columns to remove spaces and generally promote brevity.

#names(cooper_rcpts_2019A) <- c("date","prior","donor","street1","street2","city","state","zip","country","postal","profession","employer","purpose","type","account","payment_form","description","amount","sum_to_date")
```


If you wanted to find donors who work for the Universit of North Carolina at Chapel Hill.

Find all the university employers
```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(employer, "UNIVERSITY"))
```

```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(employer, "UNC"))
```



```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(employer, "U/. OF"))
```

```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(employer, "UNC") | str_detect(employer, "UNIVERSITY") | str_detect(employer, "U/. OF") )
```

```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(employer, "^UNC") | str_detect(employer, "UNIVERSITY") | str_detect(employer, "U/. OF") | str_detect(profession, "PROF"))
```
####UGH. How do you make sure UNC doesn't match BUNCOME. FIXED.

```{r}
cooper_rcpts_2019A %>%
  filter(str_detect(profession, "PROF"))
```


### JUST PROFESSORS
### ANYONE WHO WORKS AT A UNIVERSITY

### INCLUDING RETIRED PROFESSORS

###In vhis, create a new column that just stories whether it was a general election or not.

### Replace "UNC" with "UNIVERSITY OF NORTH CAROLINA" in a new column called NewEmp. (Also, note why this doesn't really work.)

```{r}
coop_new <- cooper_rcpts_2019A %>%
  mutate(NewEmp = str_replace(employer, "^UNC", "UNIVERSITY OF NORTH CAROLINA"))
```

```{r}
coop_new %>%
  filter(str_detect(employer, "^UNC") )
```


### Split donor names
```{r}
coop_new<- cooper_rcpts_2019A %>%
  filter(donor != "Aggregated Individual Contribution") %>%
  mutate(LastName = str_split(donor, " ", simplify=FALSE))
```

