---
title: "HW4: First R Markdown"
author: "FIRSTNAME LASTNAME"
date: "`r format(Sys.time(), '%B %d, %Y')`"
time: "`r format(Sys.time(), '%H:%M')`"
output: html_document
---


##Instructions
Complete this assignment in RStudio. Run all of the chunks, then Knit the markdown file to html. Upload that HTML file to the HW4 assignment on Sakai.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.Calculate how many years it has been since UNC opened its doors in 1793.
```{r}

```

### 2. Create a variable called `coach` that stores the name of the UNC women's basketball coach.
```{r}

# write your code above here
coach
```

### 3. Create a variable called `students` that stores the number of students in MEJO 570.
```{r}

# write your code above here
students
```

### 4. Create a variable called `instructors` that stores the names of the people teaching your classes this semester.

```{r}

# write your code above here
instructors
```

### 5. Create a variable called `attendance` that stores the approximate number of students your classes this semester. (You will need to create your own code chunk here.)

### 6. What is the average number of students in your classes this semester?
```{r}
mean(   )
```


### 7. Use markdown to make an unordered list of five things. Name the list using a "header". Make the third and fifth items bold. And link the second item to the UNC.edu homepage. You can use this [Markdown Cheatsheet](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet#emphasis) 


